--- 
title: "Deep Learning with Tensorflow and Keras"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: misk-data-science/misk-packages
description: "Deep Learning with Tensorflow and Keras."
---

# Welcome {-}

This module introduces the essential concepts of building deep learning models with TensorFlow and Keras. Throughout this workshop students will gain an intuitive understanding of the architectures and engines that make up deep learning models, apply a variety of deep learning algorithms (i.e. MLPs, CNNs, RNNs, LSTMs, collaborative filtering), understand when and how to tune the various hyperparameters, and be able to interpret model results. Students will have the opportunity to apply practical applications covering a variety of tasks such as computer vision, natural language processing, product recommendation and more. By the end of this module, students should have a firm grasp of deep learning and be able to implement a systematic approach for producing high quality modeling results.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

## Who should read this {-}

```{block, type='todo'}
TBD
```

This module makes a few assumptions of your established knowledge regarding your programming skills. Below are some important assumptions made and resources to read through if you feel inadequately prepared:

```{block, type='todo'}
Complete after rest of material is finalized.
```

| Assumptions                       | `r fontawesome::fa("python")` Resource | `r fontawesome::fa("r-project")` Resource   
| --------------------------------- | ------------- | ------------- |
| You should be familiar with...    |               |               | 
| You should be familiar with...    |               |               |
| You should be familiar with...    |               |               |
| You should be familiar with...    |               |               |

## What you need for this book {-}

```{block, type='todo'}
TBD
```

## Conventions used in this book {-}

The following typographical conventions are used in this book:

* ___strong italic___: indicates new terms,
* __bold__: indicates package & file names,
* `inline code`: monospaced highlighted text indicates functions or other commands that could be typed literally by the user,
* code chunk: indicates commands or other text that could be typed literally by the user

```{r, first-code-chunk, collapse=TRUE}
1 + 2
```

We will also refer to both R and Python throughout. When discussing one or the other we will typically label with the appropriate icons:

- Python: `r fontawesome::fa("python")`
- R: `r fontawesome::fa("r-project")`

In addition to the general text used throughout, you will notice the following code chunks:

```{block, type = "tip"}
Signifies a tip or suggestion
```

```{block, type = "note"}
Signifies a general note
```

```{block, type = "warning"}
Signifies a warning or caution
```

## Feedback {-}

Reader comments are greatly appreciated. To report errors or bugs please post an issue at https://github.com/misk-data-science/misk-dl/issues.

## Acknowledgments {-} 

```{block, type='todo'}
TBD
```
